\documentclass[10pt, journal]{IEEEtran}

\usepackage{url}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage[section]{placeins}
\usepackage[justification=centering]{caption}
\usepackage{calc}
\usepackage[nomessages]{fp}
\usepackage{ltxtable}
\usepackage{booktabs}
    
\usepackage[T1]{fontenc} % optional
%\usepackage[cmintegrals]{newtxmath} buggy
\usepackage{txfonts}
\usepackage{bm} % optional

\usepackage{glossaries}

\usetikzlibrary{shapes, arrows}

\makeatletter
\def\@hex@@Hex#1%
 {\if a#1A\else \if b#1B\else \if c#1C\else \if d#1D\else
  \if e#1E\else \if f#1F\else #1\fi\fi\fi\fi\fi\fi \@hex@Hex}
\makeatother

%\makeatletter
%\AtBeginDocument{%
%  \expandafter\renewcommand\expandafter\subsection\expandafter{%
%    \expandafter\@fb@secFB\subsection
%  }%
%}
%\makeatother

\makeglossaries
\loadglsentries{glsEntries}

%\usetikzlibrary{external}
%\tikzexternalize % activate!

\newlength{\smallColumnWidth}
\setlength{\smallColumnWidth}{\columnwidth-2cm}%


\definecolor{cCyan}{HTML}{8dd3c7}
\definecolor{cYellow}{HTML}{ffffb3}
\definecolor{cFlieder}{HTML}{bebada}
\definecolor{cRed}{HTML}{fb8072}
\definecolor{cBlue}{HTML}{80b1d3}
\definecolor{cOrange}{HTML}{fdb462}
\definecolor{cGreen}{HTML}{b3de69}
\definecolor{cPink}{HTML}{fccde5}

\title{Dynamic Partial Self-Reconfiguration of \\Self-Aware Systems for Fault Tolerance}
%\author{Constantin Schieber, 01228774}

\author{\IEEEauthorblockN{Constantin Schieber}
\IEEEauthorblockA{%\\Vienna University of Technology\\
\\Institute of Computer Technology\\
TU Wien, Vienna, Austria\\
Constantin.Schieber@tuwien.ac.at}
\thanks{This paper was prepared under the supervision of Dr. Nima TaheriNejad.}
}
\begin{document}
\maketitle

\begin{abstract}
    A system can be described as fault-tolerant if it can continue at the same level of performance even though one or more components have failed. 
    This property is inherently important for systems that operate without any chance of maintenance.
    \glspl{FPGA} provide the opportunity of \gls{DPR}, which provides them with the ability to efficiently react to faults that are introduced through environmental (e.g. radiation, heat) or internal (e.g. a malicious \gls{IP}) changes.
    Through the structural adaptions that are possible with \gls{DPR}, faulty chip areas can be avoided and a graceful degradation of performance with high granularity in reply to power constraints is possible.
    It also enables efficiency through selective instantiation of needed functionality.
    
    This work focuses on fault mitigation aspects of such systems. 
    It includes reviews of the types of faults that occur, methods for their detection and how certain faults can be mitigated. 
    We show that there is a wide variety of research on this topic that is especially mature in the aeronautics and space sector.
    Particularly the mitigation of faults within \glspl{FPGA} is widely researched.
    We also find that \gls{DPR} is rarely used to replace the functionality of external modules although this approach seems to provide a good base for economical redundancy solutions.
    \gls{DPR}, in general, enables a fault mitigation solution on the architectural level that enables the usage of commercial off-the-shelf hardware for uses under extreme conditions.
    
    % === Improved Version === %
    %We describe a system as fault-tolerant if it can continue at the same level of performance even though one or more components have failed.
    %This property is inherently important for systems that operate without any chance of maintenance.
    %Environmental (e.g. radiation, heat) or internal (e.g. a malicious \gls{IP}) changes are common causes for faults in hardware.
    %On \glspl{FPGA} we have the opportunity to use \gls{DPR}, which provides us with the ability to efficiently react to these faults.
    %The system can avoid faulty chip areas on the \gls{FPGA} with the help of \gls{DPR} by making structural adaptions.
    %This allows the system to gracefully degrade performance with a high granularity. 
    %It can consider and respect constraints like computing speed, power consumption and area usage during the degradation process.
    %It also increases efficiency through selective instantiation of needed functionality.
    
    %This work focuses on fault mitigation aspects of such systems. 
    %It includes reviews of the types of faults that occur, methods for their detection and how a system can mitigate certain faults. 
    %We show that there is a wide variety of research on this topic that is especially mature in the aeronautics and space sector.
    %Particularly the mitigation of faults within \glspl{FPGA} is widely researched.
    
    %We also find that \gls{DPR} is rarely used to replace the functionality of external modules although this approach seems to provide a good base for economical redundancy solutions.
    %\gls{DPR}, in general, enables a fault mitigation solution on the architectural level that enables the usage of commercial off-the-shelf hardware for uses under extreme conditions.
\end{abstract}

\input{./tex/Introduction.tex}
\input{./tex/InternalFaults.tex}
\input{./tex/ExternalFaults.tex}
\input{./tex/Conclusion.tex}


\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,SocSeminarNew}

\end{document}
